\documentclass[10pt,a4paper]{article}

\usepackage{geometry}
\geometry{margin=1.25cm}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\pagenumbering{gobble}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=*,noitemsep,topsep=1pt,parsep=0pt,partopsep=0pt}
\titlespacing*{\section}{0pt}{6pt}{2pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{-3pt}\rule{\linewidth}{0.4pt}]

\begin{document}

%--------------------
% Header
%--------------------
\begin{center}
  {\LARGE\bfseries Nikolai Nesterenko}\\[-1pt]
  Product Security Engineer \textbar{} AI Security \textbar{} Security Architecture
\end{center}

\vspace{-2pt}
\begin{center}
\faPhone*\,\href{tel:+79952318211}{+7 995 231 82 11}
\quad
\faEnvelope\,\href{mailto:nesni248@gmail.com}{nesni248@gmail.com}
\quad
\faLinkedin\,\href{https://www.linkedin.com/in/softg0th}{linkedin.com/in/softg0th}
\quad
\faTelegram\, @softg0th
\end{center}

%--------------------
% Summary
%--------------------
\section*{Summary}
Product Security Engineer with a backend engineering background. Work across AppSec, DevSecOps, security architecture, AI security and MLSecOps/LLMSecOps. Hands-on experience with code and architecture review, SAST/SCA triage, DAST, ASOC tooling, mobile security testing, IAM and AI-agent security.

%--------------------
% Experience
%--------------------
\section*{Experience}

\textbf{Yandex} \hfill Sept 2025--Present\\
\textit{Product Security Engineer}
\begin{itemize}
  \item Product security in fintech and AI security.
\end{itemize}

\textbf{Severstal} \hfill Aug 2024--Sept 2025\\
\textit{Cybersecurity Manager}
\begin{itemize}
  \item Worked on AppSec, DevSecOps and security architecture at corporate group level.
  \item Conducted code and architecture reviews, triaged SAST/SCA reports and performed manual security testing with DAST-focused tooling.
  \item Designed security requirements for infrastructure, ML systems, business applications and contractor-built software.
  \item Built the company's first MLSecOps/LLMSecOps cycle: policies, solution architectures and consultations for ML teams.
  \item Led security work for IAM and AI-agent initiatives; piloted vendor products and ran internal engineering workshops.
  \item Served on the Technical Committee and participated in technical interviews for AppSec roles.
\end{itemize}

\textbf{Alfa-Bank} \hfill Jan 2024--Mar 2024\\
\textit{DevSecOps Engineer}
\begin{itemize}
  \item Developed an in-house ASOC platform: maintained Python/FastAPI/MongoDB codebase, implemented integrations with corporate systems including Jira, fixed bugs and improved stability.
\end{itemize}

\textbf{RAMAX Group} \hfill Aug 2022--Dec 2023\\
\textit{Software Engineer}
\begin{itemize}
  \item Backend developer on a route optimisation platform: built services for time/distance matrix generation, mathematical solver backends, storage, execution and computation scheduling.
  \item Maintained and refactored a large legacy monolith; built integration tools and worked with CI/CD, Kubernetes and observability stack.
\end{itemize}

\textbf{VK} \hfill Jun 2023--Aug 2023\\
\textit{Application Security Engineer Intern}
\begin{itemize}
  \item Built an automated DAST pipeline for RuStore using OWASP ZAP API, Python, Flask and CI/CD.
  \item Tested hundreds of Android applications, performed manual checks with Burp Suite/ZAP/custom tooling and contributed to an internal MobSF fork.
\end{itemize}

%--------------------
% Other Experience
%--------------------
\section*{Other Experience}
\textbf{Social Minting} --- Developer, MusAI startup: Stable Diffusion integrations via Replicate, Appwrite-based prototyping, dataset curation.\\
\textbf{ITMO University} --- Software Engineer Intern: PostgreSQL migration, Celery/Centrifugo integration, Dockerization and backend refactoring.

%--------------------
% Education
%--------------------
\section*{Education}
\textbf{ITMO University} --- M.Sc. Software Engineering, 2024--2026\\
\textbf{ITMO University} --- B.Sc. Information Security, 2020--2024

%--------------------
% Languages
%--------------------
\section*{Languages}
Russian --- native \textbullet{} English --- B2

\end{document}
```
